%-------------------------
% Resume in LaTeX
% Author : Hayden Moritz
% Inspired By: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[11pt, letterpaper]{article}

\title{Resume}
\author{Hayden Moritz}
\date{May 24, 2022}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% Clear all header and footer fields
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Needed for fancyhdr warning
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%%%%%%%%%%%%%%%  BEGIN RESUME  %%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------
\begin{center}
	{\Huge \scshape Hayden Moritz} \\ \vspace{1pt}
	\href{mailto:me@haydenmoritz.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{me@haydenmoritz.com}} ~
	\href{https://haydenmoritz.com}{\raisebox{-0.2\height}\faGlobe\ \underline{haydenmoritz.com}}
	\vspace{-8pt}
\end{center}


%----------EXECUTIVE SUMMARY----------
\section{Executive Summary}
\begin{itemize}[leftmargin=0in, label={}]
	\small{\item{
		\textbf{}{Software Engineer with 4+ years of full-stack development experience architecting, building, and securing highly resilient web and mobile applications utilizing industry best practices. Seeking a mid-level, full-time position as a Software Engineer.} \\
	}}
\end{itemize}
\vspace{-16pt}


%----------EXPERIENCE----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer 2}{September 2021 -- Present}
{Ramsey Solutions}{Franklin, TN}
\resumeItemListStart
\resumeItem{Developed a new online marketplace platform comprising of multiple microfrontends written in TypeScript (React) which are served via a Kotlin (Spring Boot) REST API backend-for-frontend that is responsible for handling business logic and calling into numerous Java microservices that facilitate relational database (SQL) transactions.}
\resumeItem{Instituted CI/CD deployment and PR pipelines using Docker, AWS, and GitLab to promote concurrent development.}
\resumeItem{Scaled software security by implementing Tenable web security scans using Selenium browser automation.}
\resumeItem{Coordinated engineering efforts across multiple teams using the Kanban development framework.}
\resumeItemListEnd

\resumeSubheading
{Programmer Analyst}{October 2019 -- September 2021}
{Wyoming Game and Fish Department}{Cheyenne, WY}
\resumeItemListStart
\resumeItem{Architected, implemented, and scaled several secure, high-volume web applications for e-commerce, big data analytics, federated login, and more. Implemented features across the full stack from the browser to the API to the database.}
\resumeItem{Specific projects include: a federated SSO login portal for all external-facing applications, a REST API for secure data exposure to third parties, and an ASP.NET web app handling online boat registrations across the State of Wyoming.}
\resumeItemListEnd

\resumeSubheading
{Android Developer}{March 2018 -- June 2019}
{Manufacturing-Works}{Laramie, WY}
\resumeItemListStart
\resumeItem{Designed and implemented a digital enterprise resource planning (ERP) solution for a large manufacturing client.}
\resumeItem{Wrote a native Android app using Java that interfaced with a PHP REST API and persisted data in a SQL database.}
\resumeItemListEnd

\resumeSubheading
{Teaching Assistant}{August 2018 -- May 2019}
{Microsoft TEALS}{Casper, WY}
\resumeItemListStart
\resumeItem{Taught high school students programming skills and computer science fundamentals using Snap! and Python.}
\resumeItemListEnd
    
\resumeSubHeadingListEnd
\vspace{-16pt}


%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Languages}{: Kotlin, Java, C\#, Python, Ruby, Bash, SQL, HTML, CSS, JavaScript, Typescript, \LaTeX{}} \\
		\textbf{Developer Tools}{: Docker, GitHub, GitLab, IntelliJ IDEA, Android Studio, VS Code, Figma, AWS, Azure} \\
		\textbf{Technologies/Frameworks}{: Spring, Ruby on Rails, React, REST, Linux, Git, Maven, MockK, JUnit, ASP.NET, Cron} \\
	}}
\end{itemize}
\vspace{-16pt}


%----------EDUCATION & CERTIFICATIONS----------
\section{Education \& Certifications}
\resumeSubHeadingListStart

% CSSLP certification
% \resumeSubheading
% {(ISC)$^2$}{July 2022}
% {CSSLP}{}

% Alternative UWYO layout
% \resumeSubheadingSimple
% {University of Wyoming}{August 2015 -- December 2019}
% \resumeItemListStart
% \resumeItem{\textbf{Major}: Bachelor of Science in Computer Science}
% \resumeItem{\textbf{Certificate (Minor)}: Cybersecurity}
% \resumeItemListEnd

\resumeSubheading
{University of Wyoming}{December 2019}
{Cybersecurity Certificate}{Laramie, WY}

\resumeSubheading
{University of Wyoming}{August 2015 -- December 2019}
{Bachelor of Science in Computer Science}{Laramie, WY}

\resumeSubHeadingListEnd
\vspace{-16pt}

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingListStart

\vspace{-5pt}
\resumeProjectHeading
{\textbf{Pass-Through Billing Smart Contract} $|$ \emph{Haskell, Cardano, Marlowe}}{September 2021}
\resumeItemListStart
\resumeItem{Modeled pass-through billing revenue as a Cardano smart contract using Haskell within in the Marlowe environment.}
\resumeItem{Submitted to WyoHackathon 2021 and was the first place winning project.}
\resumeItemListEnd

\vspace{-13pt}

\resumeProjectHeading
{\textbf{CellSight} $|$ \emph{Python, Bash, IoT}}{April 2019}
\resumeItemListStart
\resumeItem{Developed a Raspberry Pi IoT network capable of sniffing WiFi traffic and triangulating positions from signal strength.}
\resumeItem{Interfaced with airmon-ng using Bash and parsed and aggregated the results with a Python script.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}


%----------ACHIEVEMENTS----------
\section{Achievements}
\resumeSubHeadingListStart

\resumeSubheading{Ramsey Solutions}{May 2022 -- Present}{JVM (Java/Kotlin) Language Champion}{}
\resumeSubHeadingListEnd
\resumeItemListStart
\resumeItem{Advanced JVM adoption by creating new Docker (M1) images, building project templates, and writing documentation.}
\resumeItemListEnd

\vspace{-5pt}

\resumeSubHeadingListStart
\resumeSubheading{Boy Scouts of America}{July 2015}{Eagle Scout Rank}{}
\resumeSubHeadingListEnd
\resumeItemListStart
\resumeItem{Achieved the highest possible honor in Boy Scouts after 12 years of active involvement.}

\resumeItemListEnd

\end{document}


%%%%%%%%%%%%%%%  END RESUME  %%%%%%%%%%%%%%%
